\LARGE \bf Grasp Metric for Gaussian Proccess Implicit Surface Representation of Shape Uncertainity

### 2014-07-07 paper.tex
Changed some langles, formatting, typos

\section{Related Work}

@@

\begin{equation}
  \mathcal{C} 
  =
  \frac
    {\int_{\mathcal{R}}x \mathcal{D}(x) dx}
    {\int_{\mathcal{R}}  \mathcal{D}(x) dx}
\end{equation}

@@

We follow the notation of \cite{pokorny2013classical} and we re-state some of their central theorems for our use here.
For more detail, refer there.
$Q(g)$ refers to the exact $L^1$ grasp quality.
It is denoted by the following

@@

We hence have \\

$|q(g) - q(g')| \leq Ld(g,g')$ for all $g,g' \in X$. \\

Since $Q(g) = max(0,q(g))$, $Q$ is also Lipschitz continuous with the same constant $L$ on $X$. 
\end{theorem}

\subsection{Our Extension}
Setting $l_{i,a,b} = h_{W_i(g)}(a,b)$, we have for $||(a,b)|| \leq 1$ that is $|l_{i,a,b}(g) - l_{i,a,b}(g')|$ is bounded by $|<n_i,a+b\times (c_i-z)> - <n_i',a+b\times(c_i'-z')>|+\mu|||n_i \times (a+b \times (c_i -z)|| - ||n_i \times (a + b \times (c_i' - z')) |||$, using Theorem \ref{lemma35}. By using the following facts $||a|| \leq 1$, $||b|| \leq 1$, $||v \times w || \leq ||w||||v||$, $|<v,w>| \leq ||v||||w||$, we obtain:

\begin{align*}
|l_{i,a,b}(g) - l_{i,a,b}(g')| &\leq ||n_i - n_i'||(1+||c_i - z||) \\
					&+ ||c_i - z_i - c_i'-z_i'|| \\
					&+ \mu(||n_i - n_i'||(1+||c_i - z||)\\
					&+||c_i - z_i-c_i'-z'||
\end{align*}

@@

 \begin{align*}
b_i(p) &= ||\sigma_{n_i}(p)||(1+\bar{r}|) + ||\sigma_{r_i}(p)|| \\
                                      &+ \tau(||\sigma(p)_{n_i}||(1+||\bar{r}||)+||\sigma_{r_i}(p)||)
\end{align*}

@@

 \begin{align}
 q(g) = \min{(a,b) \in \mathbb{R}^6, ||u||=1} \max{i=1,..,m} l_{i,a,b}(g)
 \end{align}

>>>>

%\section{Related Work}

@@

\begin{equation}
  \bar{z} 
  =
  \frac
    {\int_{\mathcal{R}}x \mathcal{D}(x) dx}
    {\int_{\mathcal{R}}  \mathcal{D}(x) dx}
\end{equation}

@@

We follow the notation of \cite{pokorny2013classical} except that their $\mu$ is our $\tau$ since we use $\mu$ for means.  
We re-state some of their central theorems for our use here.
For more detail, refer there.
$Q(g)$ refers to the exact $L^1$ grasp quality.
It is denoted by the following

@@

We hence have

\[
|q(g) - q(g')| \leq Ld(g,g'),\  \forall g,g' \in X.
\]

Since $Q(g) = \max(0,q(g))$, $Q$ is also Lipschitz continuous with the same constant $L$ on $X$. 
\end{theorem}

Setting $l_{i,a,b} = h_{W_i(g)}(a,b)$, we have for $||(a,b)|| \leq 1$ that is $|l_{i,a,b}(g) - l_{i,a,b}(g')|$ is bounded by $|\langle n_i,a+b\times (c_i-z)\rangle - \langle n_i',a+b\times(c_i'-z')\rangle|+\mu|||n_i \times (a+b \times (c_i -z))|| - ||n_i \times (a + b \times (c_i' - z')) |||$, using Theorem \ref{lemma35}.
By using the following facts $||a|| \leq 1$, $||b|| \leq 1$, $||v \times w || \leq ||w||||v||$, $|\langle v,w\rangle | \leq ||v||||w||$, we obtain:

\begin{align*}
|l_{i,a,b}(g) - l_{i,a,b}(g')| &\leq ||n_i - n_i'||(1+||c_i - z||) \\
					&+ ||(c_i - z)-(c_i'-z')|| \\
					&+ \mu(||n_i - n_i'||(1+||c_i - z||)\\
					&+||(c_i - z)-(c_i'-z')||)
\end{align*}

\subsection{Our Extension}

@@

 \begin{align*}
b_i(p) &= ||\sigma_{n_i}(p)||(1+||\bar{r}||) + ||\sigma_{r_i}(p)|| \\
                                      &+ \tau(||\sigma(p)_{n_i}||(1+||\bar{r}||)+||\sigma_{r_i}(p)||)
\end{align*}

@@

 \begin{align}
 q(g) = \min_{(a,b) \in \mathbb{R}^6, ||u||=1} \max_{i=1,..,m} l_{i,a,b}(g)
 \end{align}
